---
title: "Class Notes Oct 3"
author: "Nathan Bendriem"
date: "October 3, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(gapminder))

```


After going through the `dplyr` [vignette](https://cran.r-project.org/web/packages/dplyr/vignettes/two-table.html) on "two-table verbs", we'll work on the following exercises.


Consider the following areas of countries, in hectares:

```{r}
(areas <- data.frame(country=c("Canada", "United States", "India", "Vatican City"), area=c(998.5*10^6, 983.4*10^6, 328.7*10^6, 44)) %>% as.tbl)
```


1. To the `gapminder` dataset, add an `area` variable using the `areas` tibble. Be sure to preserve all the rows of the original `gapminder` dataset.

```{r}
left_join(gapminder, areas)
```


2. To the `gapminder` dataset, add an `area` variable using the `areas` tibble, but only keeping obervations for which areas are available.

```{r}
inner_join(gapminder, areas)
```
```{r}
anti_join(gapminder, areas)
```
```{r}
semi_join(areas, gapminder, join_by(country))
```
```{r}
full_join(gapminder, areas)

semi_join(gapminder, areas)
```

```


3. Use a `_join` function to output the rows in `areas` corresponding to countries that _are not_ found in the `gapminder` dataset. 

4. Use a `_join` function to output the rows in `areas` corresponding to countries that _are_ found in the `gapminder` dataset. 

5. Construct a tibble that joins `gapminder` and `areas`, so that all rows found in each original tibble are also found in the final tibble. 


6. Subset the `gapminder` dataset to have countries that are only found in the `areas` data frame. 


7. Subset the `gapminder` dataset to have countries that are _not_ found in the `areas` data frame. 
